### 2016-12-14 Objects/Objects.tex
Finishing text of objects section (pre whittling it all down and adding figures)

\subsection{Isolation}
\label{sec:objects_ele_iso}
The identification requirements discussed up to now reduce the backgrounds 
from misidentified electrons, but do not eliminate them completely. If jets are
misidentified as electrons, or an electron resulting from a heavy--flavour 
decay is identified, the electron is not isolated. Therefore requirements
on the electron isolation can reduce these backgrounds even further.
Different isolation definitions are used in \ac{CMS}, for the analyses presented
in later chapters a combined relative isolation variable is defined as:
\begin{equation}\label{eqn:electron_reliso}
I_{\text{rel}} = \frac{\Sigma p_{\text{T}}(\text{charged}) + \mathrm{max}(\Sigma E_{\text{T}}(\text{neutral}) + \Sigma E_{\text{T}}(\text{photon}) - \Delta\beta \Sigma E_{\text{T}}(\text{PU}),0)}{P_{T}^{e}},
\end{equation}
Where the \pT and \ET sums are taken within a cone in $\eta - \phi$ around the direction
of the electron, $\Delta R = 0.4$ during Run 1 and $\Delta R = 0.3$ during Run 2.
The sum over \pT$^{\text{charged}}$ corresponds to the \pT of all charged \ac{PF} 
hadrons associated with the primary vertex and within the cone of radius $\Delta R$ around
the electron's axis. The \ET$^{\text{neutral}}$ and \ET$^{\text{photon}}$ sums
run over all neutral hadronic energy and photon energy within the cone of radius $\Delta R$.
The contribution from neutral particles due to pile--up needs to be subtracted from
this term, which is estimated as the sum of charged hadronic \pT for hadrons not associated
with the primary vertex, multiplied by a $\Delta \beta$ factor of $\frac{1}{2}$.
CITE SOMETHING!

@@

The particles identified by the \ac{PF} algorithm
are clustered into jets using the anti-\kT algorithm \cite{antiKT} as implemented
in \texttt{FastJet} version 3.0.1 \cite{fastjet}. Jet clustering algorithms 
define distance parameters $d_{ij}$, denoting the distance between object (particle or cluster of 
particles) $i$ and 
object $j$, and $d_{iB}$ denoting the distance between 
object $i$ and the beam. The smallest of the distances
is defined and if this is a distance between object i and an object j, objects
i and j are combined. If $d_{iB}$ is the smallest distance, object i
is called a jet and removed from the list of objects. In the anti-\kT algorithm
these distance parameters are defined as:
\begin{align}\label{eqn:objects_antikt}
d_{ij}=\text{min}(p_{\text{T},i}^{-2},p_{\text{T},j}^{-2})\frac{\Delta_{ij}^2}{R^2}\\
d_{iB} = p_{\text{T}}^{-2},
\end{align}
where $\Delta_{ij} = \sqrt{(y_i-y_j)^2+(\phi_i - \phi_j)^2}$ is the distance
between the objects i and j in rapidity-azimuthal angle space. The radius
parameter $R$ was chosen as 0.5 during Run 1 CITATION and as 0.4 during Run 2 \cite{cms-jets-run2}. 
This algorithm is collinear-- and infrared--safe, which means that the number of jets
is not affected by the emission of soft collinear gluons or parton splitting. 
The effects of pile--up particles on the jet energy and substructure can be
mitigated using several methods. For the analysis presented in CHAPMSSM a
\ac{CHS} technique is employed \cite{cms-jets-run2}.  In this method
charged hadronic \ac{PF} candidates not associated with the primary vertex 
are not considered in the clustering. For the analysis presented in
chapter \ref{chap:hhh} a dedicated identification algorithm \cite{cms-jets-puid} 
based on vertex- and jet shape information was used to reject jets due to pile--up.

\subsection{Jet energy corrections}
\label{sec:objects_jets_jec}

\subsection{B-tagging}
\label{sec:objects_jets_btag}

\section{Missing energy}
\label{sec:objects_met}

\subsection{Recoil corrections}
\label{sec:objects_met_recoilcorr}

>>>>

\subsection{Isolation}
\label{sec:objects_ele_iso}
The identification requirements discussed up to now reduce the backgrounds 
from misidentified electrons, but do not eliminate them completely. If jets are
misidentified as electrons, or an electron resulting from a heavy--flavour 
decay is identified, the electron is not isolated. Therefore requirements
on the electron isolation can reduce these backgrounds even further.
Different isolation definitions are used in \ac{CMS}, for the analyses presented
in later chapters a combined relative isolation variable is defined as:
\begin{equation}\label{eqn:electron_reliso}
I_{\text{rel}} = \frac{\Sigma p_{\text{T}}(\text{charged}) + \mathrm{max}(\Sigma E_{\text{T}}(\text{neutral}) + \Sigma E_{\text{T}}(\text{photon}) - \Delta\beta \Sigma E_{\text{T}}(\text{PU}),0)}{P_{T}^{e}},
\end{equation}
Where the \pT and \ET sums are taken within a cone in $\eta - \phi$ around the direction
of the electron, $\Delta R = 0.4$ during Run 1 and $\Delta R = 0.3$ during Run 2.
The sum over \pT$^{\text{charged}}$ corresponds to the \pT of all charged \ac{PF} 
hadrons associated with the primary vertex and within the cone of radius $\Delta R$ around
the electron's axis. The \ET$^{\text{neutral}}$ and \ET$^{\text{photon}}$ sums
run over all neutral hadronic energy and photon energy within the cone of radius $\Delta R$.
The contribution from neutral particles due to pile--up needs to be subtracted from
this term, which is estimated as the sum of charged hadronic \pT for hadrons not associated
with the primary vertex, multiplied by a $\Delta \beta$ factor of $\frac{1}{2}$ \cite{SMHtautauCMS}.

@@

The particles identified by the \ac{PF} algorithm
are clustered into jets using the anti-\kT algorithm \cite{antiKT} as implemented
in \texttt{FastJet} version 3.0.1 \cite{fastjet}. Jet clustering algorithms 
define distance parameters $d_{ij}$, denoting the distance between object (particle or cluster of 
particles) $i$ and 
object $j$, and $d_{iB}$ denoting the distance between 
object $i$ and the beam. The smallest of the distances
is defined and if this is a distance between object i and an object j, objects
i and j are combined. If $d_{iB}$ is the smallest distance, object i
is called a jet and removed from the list of objects. In the anti-\kT algorithm
these distance parameters are defined as:
\begin{align}\label{eqn:objects_antikt}
d_{ij}=\text{min}(p_{\text{T},i}^{-2},p_{\text{T},j}^{-2})\frac{\Delta_{ij}^2}{R^2}\\
d_{iB} = p_{\text{T}}^{-2},
\end{align}
where $\Delta_{ij} = \sqrt{(y_i-y_j)^2+(\phi_i - \phi_j)^2}$ is the distance
between the objects i and j in rapidity-azimuthal angle space. The radius
parameter $R$ was chosen as 0.5 during Run 1 \cite{cms-jec-2011} and as 0.4 during Run 2 \cite{cms-jets-run2}. 
This algorithm is collinear-- and infrared--safe, which means that the number of jets
is not affected by the emission of soft collinear gluons or parton splitting. 
The effects of pile--up particles on the jet energy and substructure can be
mitigated using several methods. For the analysis presented in CHAPMSSM a
\ac{CHS} technique is employed \cite{cms-jets-run2}.  In this method
charged hadronic \ac{PF} candidates not associated with the primary vertex 
are not considered in the clustering. For the analysis presented in
chapter \ref{chap:hhh} a dedicated identification algorithm \cite{cms-jets-puid} 
based on vertex- and jet shape information was used to reject jets due to pile--up.

\subsection{Jet energy corrections}
\label{sec:objects_jets_jec}
The energy measured for a jet in the detector is usually different from 
the true particle jet at hadron level. A correction is applied to both
jets in data and jets in \ac{MC} to match the measured and true
energies as
\begin{equation}\label{eqn:objects_jec}
p_{\mu}^{\text{corr}} = \mathcal{C}\cdot p_{\mu}^{\text{raw}},
\end{equation}

where $\mathcal{C}$ is a correction factor broken down into different
components as \cite{cms-jec-2011}
\begin{equation}\label{eqn:objects_jec_corrfac}
\mathcal{C} = \text{C}_{\text{offset}}(p_{\text{T}}^{\text{raw}})\cdot
\text{C}_{\text{MC}}(p_{\text{T}}',\eta)\cdot \text{C}_{\text{rel}}(\eta)
\cdot \text{C}_{\text{abs}}(p_{\text{T}}'').
\end{equation}

Here $\text{C}_{\text{offset}}$ is an offset correction, $\text{C}_{\text{MC}}$ an
\ac{MC} calibration factor, $\text{C}_{\text{rel}}$ a relative residual correction
factor and $\text{C}_{\text{abs}}$ an absolute residual correction factor. The corrections
are applied in sequence with $p_{\text{T}}'$ the transverse momentum 
of the jet after applying the offset correction and $p_{\text{T}}''$ the \pT of the
jet after all of the preceding corrections.

The offset correction $\text{C}_{\text{offset}}$ estimates and subtracts the energy
not associated with the hard scatter. The additional energy this correction
aims to address includes contributions from electronics noise and pile--up. This is
estimated on an event--by--event basis based on the average--\pT density
per unit area $\rho$ and the area of the jet $A$ \cite{jet-area}. The factor $\rho$ includes
constributions from pile--up, electronics noise and the \ac{UE} of the hard interaction, the 
latter of which should not be corrected for and therefore the average expected contribution
from the underlying event $\rho_{<\text{UE}>}$ should be subtracted from $\rho$.

The \ac{MC} calibration factor $\text{C}_{\text{MC}}$ corrects the energy of reconstructed
jets so that is is on average equal to the energy of jets in \ac{MC} events. This
factor is measured in simulated multi--jet events, measuring the response $\mathcal{R} = \frac{p_{\text{T}}^{\text{reco}}}{p_{\text{T}}^{\text{gen}}}$
with $p_{\text{T}}^{\text{gen}}$ the generator--level \pT of the jet. The correction
factor $\text{C}_{\text{MC}}$ is defined as $\text{C}_{\text{MC}} = \frac{1}{<\mathcal{R}>}$.

A di--jet \pT-balancing technique \cite{cms-jec-2011}
is used to measure the response of a jet at any $\eta$ relative
to the jet energy response in the region $|\eta|<1.3$, such that 
the relative residual correction factor makes the response flat
as a function of $\eta$. This is achieved by requiring a reference jet
in the central region of the detector ($|\eta|<1.3$), where
the response is flat, and a probe jet at any 
$\eta$ value. The relative response, in bins of $\eta$ and \pT  is determined by
averaging the balancing function $\frac{p_{\text{T}}^{\text{probe}} - p_{\text{T}}^{\text{reference}}}{p_{\text{T}}^{\text{average}}}$.

%The central region is chosen as a reference because of the uniformity of the detector, the small variation of the jet energy response, and because it provides the highest jet pT-reach.

The absolute energy scale correction factor is designed to
make the response uniform in \pT. It is measured using the \ac{MPF} method \cite{cms-jec-2011}
 using samples of \Pphoton+jets and \PZ+jets events. This method relies on the fact that \Pphoton+jets
and \PZ+jets events have no intrinsic missing energy, and so any measured \MET
is used to calibrate the \pT response of jets in the event.

Uncertainties on the jet energy scale are propagated through to analyses
and is driven by uncertainties in the energy density used for pile--up
subtraction, the photon energy scale, and the extrapolation required in the
\ac{MPF} method.

%The track-based jet types (JPT and PF) require much smaller correction factors because the charged component of the jet shower is measured accurately in the CMS tracker which extends up to |η| = 2.4. The fast rise of the correction factor for JPT jets in the region 2.0 < |η| < 2.5 is explained by the fact that part of the jets lying in this region extends beyond the tracker coverage. For PF jets, the transition beyond the tracker acceptance is smoother because the PF candidates, which are input to the clustering of PF jets, are individually calibrated prior to the clustering. While both PF jets and JPT jets exploit the tracker measurements, the JPT jets require lower correction in the region |η| < 2.0 because the tracker inefficiency is explicitly corrected for by the JPT algorithm. In the forward region (|η| > 3.0) all three jet types converge to simple calorimetric objects and therefore require almost identical corrections.

\subsection{B-tagging}
\label{sec:objects_jets_btag}
With b--quarks appearing as final states in many of the standard model
processes being studied at the \ac{LHC}, as well as in final states
of searches for new physics, correctly identifying jets due to the hadronisation
of b--quarks is very important. As b--hadrons have a relatively
large mass of 5--6 GeV and a relatively long lifetime $\tau_B \approx 1.5$ ps \cite{pdg-2014},
they move for roughl $c\tau_B \approx 450$ $\mu$m before decaying. This means 
they produce a displaced secondary decay vertex in the inner tracker.
Algorithms for tagging b--jets usually rely on the information
from these secondary vertices.
For the analysis presented in chapter \ref{chap:hhh}
the \ac{CSV} algorithm \cite{cms-btag-paper} has been used, with the upgraded
\ac{CSV}v2 version of the algorithm \cite{cms-btag-run2} used for the analysis presented in chapter CHAPMSSM. 
The \ac{CSV} algorithm takes \ac{PF} jets with \pT$ > 20$ GeV and $|\eta|<2.4$ as input and 
defines a likelihood--based discriminator to determine 
whether a jet is likely due to a b--quark hadronisation or not.
For this algorithm, secondary vertices are reconstructed from high-purity tracks
within a cone of $\Delta R = 0.3$ around the jet axis, with quality cuts applied
to reduce contamination from decays of long--lived particles or particles due 
to interactions with the detector material. Information from the resulting
secondary vertices is combined with information from the tracks associated
with the jet into a likelihood ratio.

%The presence of a secondary vertex, and kinematic quantities associated with it, 
%are helpful in distinguishing between b-- and lighter jets. Secondary
%vertices are reconstructed by selecting high--purity tracks within
%a cone of $\Delta R = 0.3$ around the jet axis, which are
%fitted using an adaptive vertex fit as for primary vertex reconstruction (section \ref{sec:objects_tracks}).
%For the \ac{CSV} algorithm, secondary vertices need to share less than 65\% of associated tracks
%with the primary vertex, and the significance of the radial distance between the two vertices
%must exceed $3\sigma$. The flight direction of each candidate has to be within a cone
%of $\Delta R < 0.5$ around the jet direction. Secondary vertices which are more
%than 2.5 cm away from the primary vertex and whose mass is either compatible
%with that of a \PKzero or exceeds $6.5$ GeV are rejected to reduce the contamination
%from vertices produced due to interactions of particles with the detector
%material or decays of long--lived particles. The information from the selected
%secondary vertices is then combined with information about the tracks in the jet,
%to form two likelihood ratios to discriminate between b- and c- jets and 
%between b- and light jets. These likelihood ratios are combined into one
%a single discriminant.
The \ac{CSV}v2 algorithm as improved for Run 2
uses an \ac{IVF} algorithm to reconstruct secondary vertices \cite{cms-ivf}. Instead of 
using only tracks near the jet, in this algorithm all reconstructed
tracks in the event which are displaced from the primary vertex are used.
In addition, the algorithm makes use of a multilayer perceptron to combine the variables
instead of constructing and combining two likelihood ratios from the input variables \cite{cms-btag-run2}. This allows
for the addition of extra variables to discriminate between b- and other jets.

Once the discriminator has been constructed, loose- medium- and tight working points
can be determined as a minimum requirement on the discriminator such that the
probability of misidentifying light--flavour jets with \pT $ > 30$ GeV is around
10\%, 1\% and 0.1 \% respectively \cite{cms-btag-paper}.

Because not all of the input variables to the \ac{CSV} algorithm are perfectly
modelled in simulation the b--tagging efficiency for different jet
flavours is different in data and \ac{MC}. Scale factors can be detemined
as the ratio of tagging efficiencies in data and \ac{MC}, which are applied to the \ac{MC} to align
the data and \ac{MC} efficiencies. The measurements of the tagging efficiency
for genuine b--jets makes use of samples containing a muon overlapping with the jet, 
making use of the $\approx$ 11\% semileptonic branching fraction of b's. For other
ranges of jet \pT the measurement can be complemented by measurements from samples
with the kinematic signatures of \ttbar production, making use of 
the large  $\Ptop \rightarrow \PW \Pbottom$ branching ratio. Measurements
of mis--tagging efficiencies for light jets are made using negative--tagging
algorithms to select samples enriched in light jets from multijet events.

Systematic uncertainties in the scale factors arise from, amongst other things,
pile--up modelling in simulation, gluon splitting into $b\bar{b}$ pairs, track mismeasurement,
and uncertainties in the fractions of different jet types.

%Some efficiency measurements are performed using samples that include a jet with a muon within ∆R = 0.4 from the jet axis (a “muon jet”). Because the semileptonic branching fraction of b hadrons is significantly larger than that for other hadrons (about 11%, or 20% when b → c → l cascade decays are included), these jets are more likely to arise from b quarks than from another flavour.

%The combinatorial complexity of the reconstruction of the decay points (secondary vertices) of b or c hadrons is more challenging in the presence of multiple proton-proton interactions. In order to minimize this complexity a different track selection is applied. Tracks must be within a cone of ∆R = 0.3 around the jet axis with a maximal distance to this axis of 0.2 cm and pass a “high-purity” criterion [32]. The “high-purity” criterion uses the normalized χ2 of the track fit, the track length, and impact parameter information to optimize the purity for each of the iterations in track reconstruction. The vertex finding procedure begins with tracks defined by this selection and proceeds iteratively. A vertex candidate is identified by applying an adaptive vertex fit [31], which is robust in the presence of outliers. The fit estimates the vertex position and assigns a weight between 0 and 1 to each track based on its compatibility with the vertex. All tracks with weights > 0.5 are then removed from the sample. The fit procedure is repeated until no new vertex candidate can be found. In the first iteration the interaction region is used as a constraint in order to identify the prompt tracks in the jet. The subsequent iterations produce decay vertex candidates.

\section{Missing energy}
\label{sec:objects_met}
The \ac{CMS} detector is able to detect most stable and long--lived particles,
however, neutrinos and hypothetical neutral weakly interacting particles
travel straight through the detector without being recorded. These particles
will give rise to an energy imbalance in the transverse plane, and so their
presence can be inferred from missing energy \MET in the event.

The \MET is defined as $-\Sigma \vec{p}_{\text{T}}$, where
the sum runs over all final--state particles and jets in the event. This quantity
can be mismeasured due to detector inefficiencies, calorimeter energy thresholds,
the nonlinearity of the calorimeter
response for hadronic particles.

%The magnitude of the ⃗E/T can be underestimated or overestimated for a variety of reasons, including minimum energy thresholds in the calorimeters, pT thresholds and inefficiencies in the tracker, and the nonlinearity of the response of the calorimeter for hadronic particles due to its non-compensating nature. This bias is significantly reduced by correcting the pT of jets to the particle-level pT using jet energy corrections

The \MET measurement can therefore be corrected by jet energy corrections as
\begin{equation}\label{eqn:objects_met_corr}
\vec{E}_{\text{T}}^{\text{miss, corr}} = \vec{E}_{\text{T}}^{\text{miss}} - \Sigma_{jets} (\vec{p}_{\text{T,jet}}^{\text{corr}} - p_{\text{T,jet}})
\end{equation}

The \MET can also be mismeasured due to pile--up interactions, and improved
measurement of the \MET at high pile--up can be obtained by using the MVA \MET
algorithm, used for \MET reconstruction in the analyses presented in chapters \ref{chap:hhh} and 
CHAPMSSM. This algorithm computes a correction to the hadronic
recoil $\vec{u}_{\text{T}}$ reconstructed from \ac{PF} particles
\begin{equation}\label{eqn:objects_met_recoil}
\vec{u}_{\text{T}} = \vec{E}_{\text{T}}^{\text{miss}} - \Sigma \vec{p}_{\text{T}}^{lep},
\end{equation}

with $\Sigma \vec{p}_{\text{T}}^{lep}$ corresponds to the vectorial sum of the transverse momenta of the
candidate constituents selected as signal particles, the di--$\tau$ candidate in the case of \htotautau
analyses.

Two \ac{BDTs} trained on \Zmm  are used to compute this correction.
The first one corrects the direction of the hadronic recoil, the second
one uses a data sample with the corrected recoil direction to compute a correction
to the magnitued of the hadronic recoil. The BDT regression uses the magnitude of the hadronic
recoil, the azimuthal angle and scalar \pT sum of all \ac{PF} particles for several 
different \MET definitions \cite{cms-met-run1} as input. 
In the process of calculating the corrections to the hadronic recoil using the MVA \MET
algorithm, the significance of the MVA \MET is also estimated, providing an event--by--event
estimator of the likelihood that the \MET is due to unseen objects rather than induced
by mismeasurement of jet energy \cite{cms-met-run1}.

%Further corrections improve the performance of the ⃗E/T reconstruction in events with large numbers of pileup interactions. The contribution to the genuine ⃗E/T from such interactions is
close to zero, as the probability to produce neutrinos is small in inelastic pp scattering (mini- mum bias) interactions. The vectorial ⃗pT sum of charged particles is therefore expected to be well balanced by that of neutral particles. However, the nonlinearity and minimum energy thresholds in the calorimeters cause ⃗E/ T to point on average in the direction of the vectorial ⃗pT sum of neutral particles.

\subsection{Recoil corrections}
\label{sec:objects_met_recoilcorr}
To correct for the mismodelling of \MET in events without genuine \MET recoil corrections are determined. 
The hadronic recoil $\vec{u}_{\text{T}} = \vec{E}_{\text{T}}^{\text{miss}} - \Sigma \vec{p}_{\text{T},\nu/\text{leptons}}$ 
is projected onto the axes parallel $u_{\parallel}$ and perpendicular $u_{\perp}$ to the \pT of the boson producing the leptons
and neutrinos. For the analyses
presented in chapters \ref{chap:hhh} and CHAPMSSM it is measured in \Zmm events, where no neutrinos
are present. Distributions of $u_{\parallel}$ and $u_{\perp}$ are fitted both in data
and \ac{MC} events, using convolutions of gaussians. Corrections are then applied to the \ac{MC}
as
\begin{equation}\label{eqn:met_recoilcorr}
u_{\parallel,\perp}' = <u_{\parallel,\perp}>_{\text{data}} + u_{\parallel,\perp} - <u_{\parallel,\perp}>_{MC} \cdot \frac{\sigma_{\text{Data}}}{\sigma_{\text{MC}}}
\end{equation}

%Recoil corrections are applied to correct for the mismodelling of $\MET$ in events without genuine $\MET$ \cite{RecoilCorrPresentation}.
%The hadronic recoil is defined as
%$\vec{U} = \vec{E}_{\text{T}}^{mis} - \Sigma \vec{p}_{\text{T},\nu/lep}$. This recoil is projected onto the axes parallel ($U_1$) and
%orthogonal ($U_2$) to the boson $p_{\text{T}}$ and it is measured in $Z\rightarrow\mu\mu$ events, in which the $\nu$ term is 0. Events are selected
%by requiring the HLT\_IsoMu22\_v trigger in data, and opposite--sign muon pairs are selected by requiring two muons with opposite charge, passing
%the medium HIP safe muon ID, the same impact parameter cuts as in the muon selection for the analysis, $I_{rel}^{\mu} < 0.15$. The leading
%muon must have a $p_{\text{T}}$ of at least 23 GeV, with the trailing muon having a $p_{\text{T}}$ of at least 10 GeV. In addition, for data
%events the leading muon must have fired the HLT\_IsoMu22\_v trigger. The requirements on muon $\eta$ are $|\eta_1| < 2.1$ and $|\eta_2|<2.4$.
%At pair level, the two muons must be separated by $\Delta R > 0.5$, and the di-muon mass must be at least 20 GeV. Pile--up reweighting,
%the muon ID, isolation, and trigger scale factors are applied, as are the muon tracking efficiencies. The DY shape reweighting
%is applied to DY MC and top $p_{T}$ reweighting is applied to the $t\bar{t}$ MC.
%The projected hadronic recoil $U$
%is determined for both $Z\rightarrow\mu\mu$ data and MC events. A double gaussian with means symmetrically shifted away from zero is used to fit the $U_2$ component,
%with a triple  gaussians for fitting the $U_1$ component. These fits are performed in bins of $Z p_{\text{T}}$ (0-10, 10-20, 20-30, 30-50, and $ > 50$ GeV), and
%bins of number of jets (0, 1 or at least 2). $Z\rightarrow \mu\mu$ events from around the Z peak are used by requiring $70 <m_{\mu\mu} < 110 $ GeV.
%To apply the corrections, the offset $w = U{1,2} -<U_{1,2}>_{MC} $ and the recoil in MC is corrected as
%$U_{1,2}' = <U_{1,2}>_{data} + w\frac{\sigma_{data}}{\sigma_{MC}}$.

### 2016-12-14 backmatter.tex
Adding some things for H->hh/A->Zh
Updating Hhh section
Adding some more stuff
Adding latest changes to bbtautau chapter
Adding more detector stuff
More HCAL stuff
Bit more on the trigger
Adding more detector bits
Full detector chapter and first part of H->hh corrections
Fixing up detector chapter
Adding section on PF and editing tau reco section
Adding muon reconstruction section
Adding part of jets section
Finishing text of objects section (pre whittling it all down and adding figures)

%% You're recommended to use the eprint-aware biblio styles which
%% can be obtained from e.g. www.arxiv.org. The file mythesis.bib
%% is derived from the source using the SPIRES Bibtex service.
%\bibliographystyle{h-physrev}
%\bibliography{mythesis}

%% I prefer to put these tables here rather than making the
%% front matter seemingly interminable. No-one cares, anyway!
\listoffigures
\listoftables

>>>>

%% You're recommended to use the eprint-aware biblio styles which
%% can be obtained from e.g. www.arxiv.org. The file mythesis.bib
%% is derived from the source using the SPIRES Bibtex service.
\bibliographystyle{lucas_unsrt}
\bibliography{references}

%% I prefer to put these tables here rather than making the
%% front matter seemingly interminable. No-one cares, anyway!
%\listoffigures
%\listoftables

\chapter*{List of Acronyms}
\addcontentsline{toc}{chapter}{List of Acronyms}
\begin{acronym}[CERN]
\acro{MC}[MC]{Monte Carlo}
\acro{CMS}[CMS]{Compact Muon Solenoid}
\acro{LHC}[LHC]{Large Hadron Colider}
\acro{CERN}[CERN]{the European Organisation for Nuclear Research }
\acro{PS}[PS]{Proton Synchrotron}
\acro{SPS}[SPS]{Super Proton Synchrotron}
\acro{PSB}[PSB]{Proton Synchrotron Booster}
\acro{LS1}[LS1]{Long Shutdown 1}
\acro{MSSM}[MSSM]{Minimal Supersymmetric standard model}
\acro{SUSY}[SUSY]{Supersymmetry}
\acro{2HDM}[2HDM]{Two Higgs Doublet Model}
\acro{ECAL}[ECAL]{Electromagnetic calorimeter}
\acro{HCAL}[HCAL]{Hadron calorimeter}
\acro{TIB}[TIB]{Tracker Inner Barrel}
\acro{TID}[TID]{Tracker Inner Disk}
\acro{TOB}[TOB]{Tracker Outer Barrel}
\acro{TEC}[TEC]{Tracker EndCap}
\acro{EB}[EB]{ECAL Barrel}
\acro{EE}[EE]{ECAL Endcaps}
\acro{HB}[HB]{Hadron Barrel Calorimeter}
\acro{HO}[HO]{Hadron Outer Calorimeter}
\acro{HE}[HE]{Hadron Endcap Calorimeter}
\acro{HF}[HF]{Hadron Forward Calorimeter}
\acro{BSM}[BSM]{Beyond the Standard Model}
\acro{L1}[L1]{Level-1}
\acro{HLT}[HLT]{High-level trigger}
\acro{CSCs}[CSCs]{Cathode Strip Chambers}
\acro{DT}[DT]{Drift Tube}
\acro{RPCs}[RPCs]{Resistive Plate Chambers}
\acro{DAQ}[DAQ]{Data Acquisition}
\acro{WLCG}[WLCG]{Worldwide LHC Computing Grid}
\acro{RF}[RF]{radio frequency}
\acro{PF}[PF]{Particle Flow}
\acro{BDTs}[BDTs]{Boosted Decision Trees}
\acro{CTF}[CTF]{Combinatorial Track Finder}
\acro{GSF}[GSF]{Gaussian Sum Filter}
%\acro{KF}[KF]{Kalman Filter}
\acro{DA}[DA]{Deterministic Annealing}
\acro{CHS}[CHS]{Charged hadron subtraction}
\acro{CSV}[CSV]{Combined Secondary Vertex}
\acro{IVF}[IVF]{Inclusive Vertex Finder}
\acro{UE}[UE]{underlying event}
\acro{MPF}[MPF]{missing transverse energy projection fraction}
\end{acronym}
